Hydrogen Epoch of Reionization Array (HERA)

### 2016-04-08 manuscript.tex
a few typos corrected

HERA's 21\,cm measurements can be used in conjunction with our semi-analytic models to constrain the ionization history. 
The red band in Fig.~\ref{fig:IonHist} shows the forecasted 95\% confidence region derived from HERA data after marginalizing over astrophysical and cosmological parameters.
Figure~\ref{fig:paramConstraints} shows the results of a Markov Chain Monte
Carlo (MCMC) pipeline for fitting models to 21\,cm power spectrum data \citep{greig_and_mesinger2015}, which we have conservatively limited to the range $8 < z < 10$ (although in practice a much broader bandwidth will be available; see Table \ref{tab:BasicParameters}).
Based on the excursion-set formalism of
\citet{furlanetto_et_al2004} and the 21cmFAST code \citep{mesinger_et_al2011},
this code models the astrophysics of
reionization with three free parameters (see Figure~\ref{fig:paramConstraints} for details). 
While the existing experiment with the most collecting area, 
the LOw Frequency ARray (LOFAR; \citealt{2013A&A...556A...2V, yatawatta_et_al2013}),
faces large
uncertainties [[[change this?]]], 
HERA's tight constraints on these parameters are comparable
to what could be achieved with the SKA.  Such results would be valuable for
informing the design and science case of the low-frequency SKA, highlighting areas where the SKA has unique capability.
Additionally, HERA's constraints enable principal component parameterizations of the
sky-averaged $21\,\textrm{cm}$ signal measurements pursued by experiments such as EDGES, increasing their signal-to-noise and thus their science return \citep{liu_parsons2015}.

@@

\section{Measuring the EOR}
\label{sec:eormeas}
Due to the expansion of the Universe over cosmological time, we can identify and measure the early Universe via the red-shift of spectral lines.  The hydrogen hyperfine transition at a rest frequency of 1420 MHz is a key spectral line due to the ubiquity of hydrogen and, being a ``forbidden'' transition, the optical depth lets us see through the entire Universe back almost to the period of recombination.  The bandwidth
therefore equates to a cosmic distance along the site of the telescope, with the frequency determining the cosmic age.  An observation of an area of sky over a given bandwidth is therefore providing an average
over a cosmic volume.

@@

\subsection{Frequency and Bandwidth}
Figure \ref{fig:cosmos} indicates the frequency range requirement to probe the expected timescale of the epoch of reionization using the 21cm line of hydrogen as the probe.  
These limits are derived from to-date complementary probes of reionization which include measurements of
the optical depth to last scattering in the CMB, QSO spectra, Ly-$\alpha$
absorption in the spectra of quasars and gamma ray bursts and the demographics
of Ly-$\alpha$ emitting galaxies
(Figure~\ref{fig:IonHist}). 
Constraints from these probes are still weak:
Ly-$\alpha$ absorption saturates at very small neutral fractions; galaxy
surveys directly constrain only the bright end of the luminosity function and
depend on an unknown escape fraction of ionizing photons to constrain
reionization; CMB measurements probe an integral quantity subject
to large degeneracies. Even when these observations are
combined into a single 95\% confidence region, the bounds remain weak.
For example, $x_{HI}$ spans almost the entire allowable range of [0,1]
at $z=8$. 21\,cm reionization experiments place much tighter constraints on ionization, with the
red band showing the forecasted 95\% confidence region derived from HERA data,
after marginalizing over astrophysical and cosmological parameters.

>>>>

HERA's 21\,cm measurements can be used in conjunction with our semi-analytic models to constrain the ionization history. 
The red band in Fig.~\ref{fig:IonHist} shows the forecasted 95\% confidence region derived from HERA data after marginalizing over astrophysical and cosmological parameters.
Figure~\ref{fig:paramConstraints} shows the results of a Markov Chain Monte
Carlo (MCMC) pipeline for fitting models to 21\,cm power spectrum data \citep{greig_and_mesinger2015}, which we have conservatively limited to the range $8 < z < 10$ (although in practice a much broader bandwidth will be available; see Sec. \ref{sec:freqs}).
Based on the excursion-set formalism of
\citet{furlanetto_et_al2004} and the 21cmFAST code \citep{mesinger_et_al2011},
this code models the astrophysics of
reionization with three free parameters (see Figure~\ref{fig:paramConstraints} for details). 
While the existing experiment with the most collecting area, 
the LOw Frequency ARray (LOFAR; \citealt{2013A&A...556A...2V, yatawatta_et_al2013}),
faces large
uncertainties [[[change this?]]], 
HERA's tight constraints on these parameters are comparable
to what could be achieved with the SKA.  Such results would be valuable for
informing the design and science case of the low-frequency SKA, highlighting areas where the SKA has unique capability.
Additionally, HERA's constraints enable principal component parameterizations of the
sky-averaged $21\,\textrm{cm}$ signal measurements pursued by experiments such as EDGES, increasing their signal-to-noise and thus their science return \citep{liu_parsons2015}.

@@

\section{Measuring the EOR}
\label{sec:eormeas}
Due to the expansion of the Universe over cosmological time, we can identify and measure the early Universe via the red-shift of spectral lines.  The hydrogen hyperfine transition at a rest frequency of 1420 MHz is a key spectral line due to the ubiquity of hydrogen and, being a ``forbidden'' transition, the optical depth lets us see through the entire Universe back almost to the period of recombination.  The bandwidth
therefore equates to a cosmic distance along the line-of-site of the telescope, with the frequency determining the cosmic age.  An observation of an area of sky over a given bandwidth is therefore providing an average
over a cosmic volume.

@@

\subsection{Frequency and Bandwidth}
\label{sec:freqs}
Figure \ref{fig:cosmos} indicates the frequency range requirement to probe the expected timescale of the epoch of reionization using the 21cm line of hydrogen as the probe.  
These limits are derived from to-date complementary probes of reionization which include measurements of
the optical depth to last scattering in the CMB, QSO spectra, Ly-$\alpha$
absorption in the spectra of quasars and gamma ray bursts and the demographics
of Ly-$\alpha$ emitting galaxies
(Figure~\ref{fig:IonHist}). 
Constraints from these probes are still weak:
Ly-$\alpha$ absorption saturates at very small neutral fractions; galaxy
surveys directly constrain only the bright end of the luminosity function and
depend on an unknown escape fraction of ionizing photons to constrain
reionization; CMB measurements probe an integral quantity subject
to large degeneracies. Even when these observations are
combined into a single 95\% confidence region, the bounds remain weak.
For example, $x_{HI}$ spans almost the entire allowable range of [0,1]
at $z=8$. 21\,cm reionization experiments place much tighter constraints on ionization, with the
red band showing the forecasted 95\% confidence region derived from HERA data,
after marginalizing over astrophysical and cosmological parameters.
